Parallel Information Set Generation for Kriegspiel

### 2012-07-12 sbac/paper.tex

\section{Introduction}
In imperfect information games, players do not have access to full knowledge of
the world. Examples of imperfect information include hidden cards in
Poker~\cite{billings02challenge} or Bridge~\cite{ginsberg96partition}, hidden
tiles in Scrabble~\cite{richards07opponent}, or hidden pieces 
Kriegspiel (partially observable chess)~\cite{li94chess}. The game tree nodes
that are indistinguishable to a player because they differ only in the
information that is hidden to the player by rule compose that player's {\em
information set.}  The ability to estimate the value of the possible states and
to reason about the probability distribution over those states is crucial to
playing imperfect information games well~\cite{thielscher12hyperplay}.

>>>>

\section{Introduction}
In imperfect information games, players do not have access to full knowledge of
the world. Examples of imperfect information include hidden cards in
Poker~\cite{billings02challenge} or Bridge~\cite{ginsberg96partition}, hidden
tiles in Scrabble~\cite{richards07opponent}, or hidden pieces 
Kriegspiel (partially observable chess)~\cite{li94chess}. The game tree nodes
that are indistinguishable to a player because they differ only in the
information that is hidden to the player by rule compose that player's {\em
information set.}  The ability to estimate the value of the possible states and
to reason about the probability distribution over those states is crucial to
playing imperfect information games well~\cite{schofield12hyperplay}.
